Location of Marine fish - general Farms

### 2021-04-27 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
added a script for summary stats for paper. Added a script to match sources and data years (or lack thereof) to every farm mapped

## now lets do the locations that have some information regarding number of farms 
gapfill_2.5 <- all_number_2.5 %>%
  left_join(bivalve_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  mutate(num_additional_farms = num_additional_farms + n_existing_farms) %>% 
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

>>>>

## now lets do the locations that have some information regarding number of farms 
gapfill_2.5 <- all_number_2.5 %>%
  left_join(bivalve_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  mutate(num_additional_farms = num_additional_farms + n_existing_farms) %>% 
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = ifelse(iso3c == "IND", 0, 1)) %>%
  filter(num_additional_farms != 0)

### 2021-04-27 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
finished datachecking my end
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now
added a script for summary stats for paper. Added a script to match sources and data years (or lack thereof) to every farm mapped

@@

@@

Source:
National Aquaculture Group, n.d. [Accessed November 12, 2020]. http://www.naqua.com.sa/about-us.php

@@

                              lon = c(120.1486974182384, 120.14508600806049, 120.13344924193156, 120.12923593005728, 120.11007291797651, 120.10560972235575, 120.09462339467383, 120.08741361713255, 120.0340739167051, 120.0323838672442, 120.19480335124462, 120.19703494905501, 120.19737827179506, 120.19960986960544, 120.48594464702815, 120.48934227493775, 120.4981761075027, 120.50893526254974, 120.51527750131434, 120.51890163775126, 121.13759861706552, 121.14388413948092, 121.14975973652137, 121.15167272160434, 121.15631854252005, 121.16246742314381, 121.3724851599623, 121.38612214670725, 121.39450636818748, 121.4097595903985, 121.40864842851558, 121.40026420703533, 121.83377270959099, 121.83292494893261, 121.83961283857079, 121.82878034126954, 121.8381057085115, 121.83829409976889, 121.87509035189372, 121.87405621071602, 121.84309342644401, 121.80292466585698))
```

@@

```{r}
grouper_points <- data.frame(lat = c(23.366020730714546, 23.344101510137286, 23.11902593130365, 23.124310527454163, 23.130061175003874, 22.412837508670247, 22.5060215233288, 22.495712950055186, 22.489210224135196, 22.478900398348003, 22.963578173481825, 22.958915389973615, 22.958796842534618, 22.95887587417216, 22.962708853156307, 22.910490254668936, 22.900053951559105, 22.88771910346936, 22.87475049020418, 22.85735162493687, 23.033784880994748, 23.01988231566828, 22.990894265701648, 22.969242998130003),
                             lon = c(120.12803212666465, 120.11599409273818, 120.05874863883409, 120.07531112355083, 120.08122629666394, 120.5141089682018, 120.361518692894, 120.37199003646582, 120.38503630058813, 120.40220243759113, 120.16265849315296, 120.16450385288077, 120.16420344548321,  120.16630629726609, 120.16480426027832, 120.17469982002679, 120.17658809509712, 120.18208125893808, 120.18637279318882, 120.18688777729894, 120.07405573439489, 120.09946161715932, 120.14268135694375, 120.15847420298654))

@@

farms_twn <-  st_as_sf(all_points_twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

@@

Source:
Martec Industries Aquaculture , n.d. . Martec.  https://www.martec.co.cr/#aquaculture

>>>>

test <- farms_eu_final %>%
  group_by(iso3c) %>%
  summarise(n())
```

@@

Source:
NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/

@@

Source:
National Aquaculture Group, 2020. [Accessed November 12, 2020]. http://www.naqua.com.sa/about-us.php

@@

                              lon = c(120.1486974182384, 120.14508600806049, 120.13344924193156, 120.12923593005728, 120.11007291797651, 120.10560972235575, 120.09462339467383, 120.08741361713255, 120.0340739167051, 120.0323838672442, 120.19480335124462, 120.19703494905501, 120.19737827179506, 120.19960986960544, 120.48594464702815, 120.48934227493775, 120.4981761075027, 120.50893526254974, 120.51527750131434, 120.51890163775126, 121.13759861706552, 121.14388413948092, 121.14975973652137, 121.15167272160434, 121.15631854252005, 121.16246742314381, 121.3724851599623, 121.38612214670725, 121.39450636818748, 121.4097595903985, 121.40864842851558, 121.40026420703533, 121.83377270959099, 121.83292494893261, 121.83961283857079, 121.82878034126954, 121.8381057085115, 121.83829409976889, 121.87509035189372, 121.87405621071602, 121.84309342644401, 121.80292466585698)) %>%
  mutate(source = "Lee")
```

@@

```{r}
grouper_points <- data.frame(lat = c(23.366020730714546, 23.344101510137286, 23.11902593130365, 23.124310527454163, 23.130061175003874, 22.412837508670247, 22.5060215233288, 22.495712950055186, 22.489210224135196, 22.478900398348003, 22.963578173481825, 22.958915389973615, 22.958796842534618, 22.95887587417216, 22.962708853156307, 22.910490254668936, 22.900053951559105, 22.88771910346936, 22.87475049020418, 22.85735162493687, 23.033784880994748, 23.01988231566828, 22.990894265701648, 22.969242998130003),
                             lon = c(120.12803212666465, 120.11599409273818, 120.05874863883409, 120.07531112355083, 120.08122629666394, 120.5141089682018, 120.361518692894, 120.37199003646582, 120.38503630058813, 120.40220243759113, 120.16265849315296, 120.16450385288077, 120.16420344548321,  120.16630629726609, 120.16480426027832, 120.17469982002679, 120.17658809509712, 120.18208125893808, 120.18637279318882, 120.18688777729894, 120.07405573439489, 120.09946161715932, 120.14268135694375, 120.15847420298654)) %>%
  mutate(source = "Kuo")

@@

farms_twn <-  st_as_sf(all_points_twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant") %>%
  dplyr::select(-source)

@@

## Save a file with the sources so we can match the sources to the correct point later
farms_twn_source <-  st_as_sf(all_points_twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

## write to farms folder 
write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/taiwan_farms_sources.csv"))

@@

Source:
Martec Industries Aquaculture , 2020. Martec.  https://www.martec.co.cr/#aquaculture
